Ion Scattering by Solar Wind Discontinuities

### 2025-03-13 notebooks/102_results_scattering.qmd
update scattering

```{julia}
include("../src/main.jl")
using Dates
using Beforerr
using FHist
using AlgebraOfGraphics: aog_theme

@@

```{julia}
# velocity v is normalized to $v0 = l Ω$, where $l$ represents the width of the RD and $Ω = q B/(mpc)$ is the cyclotron frequency.
using Unitful: ε0, μ0, mp
q_G = q / sqrt(4π * ε0)
B_G_factor = sqrt(4π / μ0)

@@

let
    h3d1 = hist3dbin(subset(df, :accuracy))
    h3d2 = hist3dbin(subset(df, :accuracy => ByRow(!)))
    z = zeros(eltype(bincounts(h3d1)))
    axis = (; aspect=:equal, xlabel="Log10 (He)", ylabel="In-plane rotation angle", zlabel="Azimuthal angle")

    f = Figure(; size=(600, 300), figure_padding=0)
    ax1 = Axis3(f[1, 1]; axis..., title="Reliable", protrusions=(30, 0, 60, 30))
    volume!(ax1, to_endpoints.(h3d1.binedges)..., replace(bincounts(h3d1), z => NaN))
    ax2 = Axis3(f[1, 2]; axis..., title="unreliable", protrusions=0)
    volume!(ax2, to_endpoints.(h3d2.binedges)..., replace(bincounts(h3d2), z => NaN))
    f
end

>>>>

```{julia}
include("../src/main.jl")
using Dates
using Beforerr
using GLMakie
using FHist
using AlgebraOfGraphics: aog_theme

@@

```{julia}
# velocity v is normalized to $v0 = l Ω$, where $l$ represents the width of the RD and $Ω = q B/(mpc)$ is the cyclotron frequency.
using Unitful: ε0, μ0, mp, q, c
q_G = q / sqrt(4π * ε0)
B_G_factor = sqrt(4π / μ0)

@@

let
    h3d1 = hist3dbin(subset(df, :accuracy))
    h3d2 = hist3dbin(subset(df, :accuracy => ByRow(!)))
    z = zeros(eltype(bincounts(h3d1)))
    # axis = (; aspect=:equal, xlabel=L"\log (ṽ_B)", ylabel="In-plane rotation angle", zlabel="Azimuthal angle")
    axis = (; aspect=:equal, xlabel=L"\log (ṽ_B)", ylabel=L"ω_{in}", zlabel=L"θ")

    f = Figure(; size=(600, 300), figure_padding=0)
    ax1 = Axis3(f[1, 1]; axis..., title="Reliable", protrusions=(30, 0, 60, 30))
    volume!(ax1, to_endpoints.(h3d1.binedges)..., replace(bincounts(h3d1), z => NaN))
    # volume!(ax1, h3d1)
    ax2 = Axis3(f[1, 2]; axis..., title="Unreliable", protrusions=0)
    p = volume!(ax2, to_endpoints.(h3d2.binedges)..., replace(bincounts(h3d2), z => NaN))
    Colorbar(f[1, 3], p)
    # volume!(ax2, h3d2)
    f
end
